Combining living and fossil taxa into phylogenies: the missing data issue

### 2014-05-27 Manuscript/TEM_draft.tex
Table RPBTC corrections

\begin{table}[ht]
\caption{Anova results: difference between 100 replicates using the RPBTC method}
\centering
\begin{tabular}{rllrrrr}
  \hline
  Tree.Type & Used.metric & Replicates & Df & F.value & p.value \\ [0.5ex]
  \hline
  Low Score & RF & 100.00 &   1 & 0.07 & 0.79 \\ [0.5ex]
  Low Score & Tr & 100.00 &   1 & 0.33 & 0.56 \\ [0.5ex]
  Medium Score & RF & 100.00 &   1 & 1.07 & 0.30 \\ [0.5ex]
  Medium Score & Tr & 100.00 &   1 & 0.00 & 0.96 \\ [0.5ex]
  High Score & RF & 100.00 &   1 & 0.20 & 0.66 \\ [0.5ex]
  High Score & Tr & 100.00 &   1 & 0.61 & 0.43 \\ [0.5ex]
  \hline
\end{tabular}
\label{RPBTC_testing}
\end{table}

>>>>

\begin{table}[ht]
\caption{Anova results: difference between 100 replicates using the RPBTC method}
\centering
\begin{tabular}{rllrrrr}
  \hline
  Tree.Type & Used.metric & Replicates & Df & F.value & p.value \\ 
  \hline
  Low Score & RF & 100.00 & 99.00 & 0.74 & 0.98 \\ 
  Low Score & Tr & 100.00 & 99.00 & 0.97 & 0.58 \\ 
  Medium Score & RF & 100.00 & 99.00 & 0.64 & 1.00 \\ 
  Medium Score & Tr & 100.00 & 99.00 & 0.45 & 1.00 \\ 
  High Score & RF & 100.00 & 99.00 & 0.20 & 1.00 \\ 
  High Score & Tr & 100.00 & 99.00 & 0.37 & 1.00 \\ 
  \hline
\end{tabular}
\end{table}
\label{RPBTC_testing}
